---
title: "Lab 00 - Hello IDS!"
author: "Ben W"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Sophie", "Ben", "Stewart", 
           "Magnus", "Toby"),
  github_username = c("Sophie", "BWipat", "stuart620", 
                      "MagnusBryce", "Toby"), 
  colour = c("purple", "royalblue", "blue", 
             "lightblue", "magenta"),
  hobby = c("sleeping", "climbing", "running", 
            "swimming", "running"),
  favourite_number = c(7, 15, 6, 4, 8)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


This plot shows my group members' GitHub usernames listed along the x axis, with a scale up the y axis labelled favourite number. A bar graph is generated with the colour corresponding to each member's favourite colour and height corresponding to favourite number. 

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "GitHub Username", 
          y = "Favourite Number",
          title = "Favourite Numbers of Workshop group 2")
```

Labs function allows labelling of axes on charts. 


### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

A pie chart might be a more suitable alternative for representing the data here?
